Downstream analysis: A pipeline to analyse time-course gene expression data

### 2019-03-06 scripts/04_downstream_analysis.Rmd
FIX looping over pre-defined ontologies

cluster = c(1, 2, 3)
ontologies = c("BP", "NF", "CC")
# It's taking too long to compile with everything. Just limit ourselves for
# now to BP
ontologies = c("BP")
all_go_terms = data.frame()
for(cluster in clusters){
    for(ontology in c("BP", "NF", "CC")){ 
	scores = as.numeric(labels == cluster)
	names(scores) = gene_names
	go_terms_enriched = find_enriched_go_terms(
	    scores,
	    gene_id_go_mapping)

>>>>

cluster = c(1, 2, 3)
ontologies = c("BP", "NF", "CC")
# It's taking too long to compile with everything. Just limit ourselves for
# now to BP
ontologies = c("BP")
all_go_terms = data.frame()
for(cluster in clusters){
    for(ontology in ontologies){ 
	scores = as.numeric(labels == cluster)
	names(scores) = gene_names
	go_terms_enriched = find_enriched_go_terms(
	    scores,
	    gene_id_go_mapping, ontology=ontology)
